Compositional equivalences based on Open pNets

### 2020-06-12 2016-Weak-FH-Bisim/WeakBisim.tex
Changes pages 22 and 73-76

$post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
= (\texttt{s\_ec}\gets \texttt{s\_ec}+1)$.
\footnote{when showing  the result of $Posts$ composition, we will Z omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}
\medskip

@@

We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}) :

\TODO{Qu'est-ce qu'on avait dit ici pour "$n$" ? a droite ou a gauche, mais pas les deux ?Et est-ce qu'on le laisse en italique dans les expressions, pour souligner son statut de parametre ?.
Dans tous les cas expliquer ?}
\smallskip

@@

$ WI_3(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
  {000 \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
        $$\forall n\ge 0$

$ WI_4(n) = \openrule
         {\{\}, True, 
   (\texttt{m\_msg}\!\gets\! \texttt{s\_msg}, \texttt{m\_ec}\!\gets\! \texttt{s\_ec}+n, \texttt{s\_ec}\!\gets\! \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\tau} 210}
        $$\forall n\ge 0$

$ WI_{456}(n) = \openrule
         {\{\}, True, 
    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
  {100 \OTWeakarrow {\tau} 100}
        $$\forall n\ge 0$

   \medskip     
The  \Post~of of the weak OT $ WI_{6a}$ is:\\

$
\begin{array}{ll}
Post_{6a}= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6} =&  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
\shortotimes \\ &(\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) =\\
&(\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
\end{array}$\\

\begin{align*}
WI_{6a}(n) =& \openrule
         {\{\}, True, 
         (\texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {220 \OTWeakarrow {\tau} 210} \forall n\ge 0
\\Post_{8c}=& post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
= (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0\\ 
WI_{8c}(n) =& \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n)}
         {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0
\end{align*}

@@

\TODO{Je ne peux pas refaire tourner le code, il faut que je modifie le pNet Editor pour qu'ils n'utilise plus les variables d'etat... Donc les 3 prochaines pages sont obsoletes...}
%% \TODO{keep ?}
%% \paragraph{Variable management.}
%% The variables in each synchronisation vector are considered local:
%% for a given pNet expression, we must have fresh local variables for
%% each occurrence of a vector (i.e. each time we instantiate rule
%% \TrDeux). Similarly the state variables of each copy of a
%% given pLTS in the system, must be distinct, and those created for each
%% application of \TrDeux\ have to be fresh and all distinct. 
%% This is implemented within the open-automaton generation algorithm,
%% using name generation using a global counter as a suffix.

@@

pLTS M1
  initial a0
  vars ?msg:Data ?c:Int
%vars a1_msg:Data a1_ec:Int
vars m_msg:Data m_ec:Int

@@

pLTS Sender
  initial s0
  vars ?msg:Data
%vars s1_msg:Data s1_ec:Int
%vars  s2_ec:Int
vars  s_msg:Data s_ec:Int

@@

pLTS Receiver
  initial r0
  vars ?msg:Data ?c:Int
%vars r1_msg:Data r1_ec:Int
vars r_msg:Data r_ec:Int

@@

Finaly, we list here in raw format, the 19 OTs computed by the tool for the SimpleProtImpl pNet.
This view uses variable names very close to the internal representation in the tool, allowing for traceability of generated fresh variables. For example:
\begin{itemize}
\item m:SV6:1:1 refers to a variable named ``m'' in the synchronisation vector ``SV6''; the last 2 numbers allows to distinguish different clones.
\item the other variable names reflect our naming policy: state variables are prefixed by the name of the state, holes actions by the name of the hole.
\end{itemize}

\TODO{To be updated completely, or removed ???}

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]

{P|->p_send(m:SV6:1:1)},
[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_ec := 0}
	OT:1 ------------------------------------------------------------
		<s0_a0_r0>-----_in(m:SV6:1:1)_----><s1_a0_r0>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))], {}
	OT:2 ------------------------------------------------------------
		<s0_a0_r0>-----p_a:SV7:1:2----><s0_a0_r0>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:3 ------------------------------------------------------------
		<s0_a0_r0>-----q_a:SV9:1:4----><s0_a0_r0>

INFO  SimpleProtImpl2 - 
{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:4 ------------------------------------------------------------
		<s1_a0_r0>-----p_a:SV7:1:2----><s1_a0_r0>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:5 ------------------------------------------------------------
		<s1_a0_r0>-----q_a:SV9:1:4----><s1_a0_r0>

{},   [(s1_msg=m:SV1:114:2)/\(s1_ec=c:SV1:114:2)
  /\((s_send(s1_msg, s1_ec))=(s_send(m:SV1:114:2, c:SV1:114:2)))
  /\(msg=m:SV1:114:2)/\(c=c:SV1:114:2)
  /\((m_recv(msg, c))=(m_recv(m:SV1:114:2, c:SV1:114:2)))],
{s2_ec := s1_ec, a1_msg := msg, a1_ec := c}
	OT:6 ------------------------------------------------------------
		<s1_a0_r0>-----_tau_----><s2_a1_r0>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:7 ------------------------------------------------------------
		<s2_a1_r0>-----p_a:SV7:1:2----><s2_a1_r0>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:8 ------------------------------------------------------------
		<s2_a1_r0>-----q_a:SV9:1:4----><s2_a1_r0>

{},   [(a1_msg=m:SV2:114:3)/\(a1_ec=c:SV2:114:3)
  /\((m_send(a1_msg, a1_ec))=(m_send(m:SV2:114:3, c:SV2:114:3)))
  /\(msg=m:SV2:114:3)/\(c=c:SV2:114:3)
  /\((r_recv(msg, c))=(r_recv(m:SV2:114:3, c:SV2:114:3)))],
{r1_msg := msg, r1_ec := c}
	OT:9 ------------------------------------------------------------
		<s2_a1_r0>-----_tau_----><s2_a0_r1>

		{},   [],   {}
	OT:10 ------------------------
		<s2_a1_r0>-----_tau_----><s2_a2_r0>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:11 ------------------------------------------------------------
		<s2_a0_r1>-----p_a:SV7:1:2----><s2_a0_r1>

{Q|->q_recv(m:SV8:1:3, c:SV8:1:3)},
[(r1_msg=m:SV5:18:6)/\(r1_ec=c:SV5:18:6)
  /\((r_send(r1_msg, r1_ec))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
	OT:12 ------------------------------------------------------------
		<s2_a0_r1>-----_out(m:SV8:1:3, c:SV8:1:3)_----><s2_a0_r2>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:13 ------------------------------------------------------------
		<s2_a0_r1>-----q_a:SV9:1:4----><s2_a0_r1>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:14 ------------------------------------------------------------
		<s2_a2_r0>-----p_a:SV7:1:2----><s2_a2_r0>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:15 ------------------------------------------------------------
		<s2_a2_r0>-----q_a:SV9:1:4----><s2_a2_r0>

		{},   [],   {s1_ec := s2_ec+1}
	OT:16 --------------------------------------
		<s2_a2_r0>-----_tau_----><s1_a0_r0>

{P|->p_a:SV7:1:2},
[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
	OT:17 ------------------------------------------------------------
		<s2_a0_r2>-----p_a:SV7:1:2----><s2_a0_r2>

{Q|->q_a:SV9:1:4},
[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
	OT:18 ------------------------------------------------------------
		<s2_a0_r2>-----q_a:SV9:1:4----><s2_a0_r2>

		{},   [],   {}
	OT:19 ------------------------
		<s2_a0_r2>-----_tau_----><s0_a0_r0>

Assignements of state variables:

Global State: <s0_a0_r0>
===================
pLTS States: <s0 vars: {}> <a0 vars: {}> <r0 vars: {}>

Global State: <s1_a0_r0>
===================
pLTS States: <s1 vars: { s1_msg <-{msg} s1_ec <-{0, s2_ec+1}}> <a0 vars: {}> <r0 vars: {}>

Global State: <s2_a1_r0>
===================
pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a1 vars: { a1_msg <-{msg} a1_ec <-{c}}> <r0 vars: {}>

Global State: <s2_a0_r1>
===================
pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r1 vars: { r1_ec <-{c} r1_msg <-{msg}}>

Global State: <s2_a2_r0>
===================
pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a2 vars: {}> <r0 vars: {}>

Global State: <s2_a0_r2>
===================
pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r2 vars: {}>

INFO  SimpleProtImpl2 - Total: 19 SATISFIABLE OTs
INFO  SimpleProtImpl2 -        185 UNSATISFIABLE OTs
INFO  SimpleProtImpl2 - Total Time: 1105 ms

@@

It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviours.
More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
In this configuration we can guarantee that they are Weak bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this 
equivalence class of states as $\{000,202\}$.
\TODO{May be express this property more formerly, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}

Details of the weak transitions is listed here:

@@

All following transitions are parametrized by an arbitrary non-negative integer $n\in \mathcal{N}$.

@@

$ WI_5(n) = \openrule
         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {210 \OTWeakarrow {\tau} 220}
         \ \forall n\ge 0$

$ WI_{5a}(n) = \openrule
         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
         {210 \OTWeakarrow {\tau} 100}
         \ \forall n\ge 0$

@@

\medskip
$ WI_7(n) = \openrule
         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
         {210 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ WI_{7a}(n) = \openrule
         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{m\_ec}+n)}
         {220 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 0$

$ WI_{7b}(n) = \openrule
         {\{\}, True, (\texttt{r\_msg}\gets \texttt{m\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\tau} 201}
         \ \forall n\ge 1$

$ WI_8 = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec)}\}, True, ()}
         {201 \OTWeakarrow {\nounderline{\texttt{out(r1-msg,r1-ec)}}} \{202, 000\}}
         \ \forall n\ge 0$

$ WI_{8a}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(m\_msg,m\_ec}+n)\}, True, ()}
         {210 \OTWeakarrow {\nounderline{\texttt{out(m\_msg,m\_ec}+n)}} \{202, 000\}}
         \ \forall n\ge 1$

 $ WI_{8b}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s\_ec}+n)\}, True, ()}
         {220 \OTWeakarrow {\nounderline{\texttt{out(??\_msg,m\_ec}+n)}} \{202, 000\}}
         \ \forall n\ge 1$

 $ WI_{8c}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, ()}
         {100 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} \{202, 000\}}
         \ \forall n\ge 1$

@@

\bigskip
Considering the first triple <b0, 000, True>, we will prove the following properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense of definition \ref{def-Weak-bisim} by the weak transition $WOT$ (it could be a set, but this will not be used here):

@@

       Full list of WOTs

>>>>

$post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
= (\texttt{s\_ec}\gets \texttt{s\_ec}+1)$.
\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}
\medskip

@@

We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}) :
As we have seen above, the effect of rule $WT_3$ when a silent action have an effect on the variable $ec$ will generate an infinite family of WOTs, depending on the number of iterations through the loops. We denote these families using a "meta-variable" $n$, ranging over $\mathcal{N}$.
% \TODO{Qu'est-ce qu'on avait dit ici pour "$n$" ? a droite ou a gauche, mais pas les deux ?Et est-ce qu'on le laisse en italique dans les expressions, pour souligner son statut de parametre ?.
% Dans tous les cas expliquer ?}
\smallskip

@@

$ \forall n\ge 0. WI_3(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
  {000 \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
        $

$  \forall n\ge 0. WI_4(n) = \openrule
         {\{\}, True, 
   (\texttt{m\_msg}\!\gets\! \texttt{s\_msg}, \texttt{m\_ec}\!\gets\! \texttt{s\_ec}+n, \texttt{s\_ec}\!\gets\! \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\tau} 210}
        $

$  \forall n\ge 0. WI_{456}(n) = \openrule
         {\{\}, True, 
    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
  {100 \OTWeakarrow {\tau} 100}
        $

   \medskip     
The  \Post~of the weak OT $ WI_{6a}$ is:\\

$
\begin{array}{ll}
Post_{6a}&= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6}\\ 
&=  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
&= (\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
\end{array}
$

So we get:

$ \forall n\ge 0. WI_{6a}(n) = \openrule
         {\{\}, True, 
         (\texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
         {220 \OTWeakarrow {\tau} 210}$

%\begin{align*}
%\\Post_{8c}=& post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
%= (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0\\ 
%WI_{8c}(n) =& \openrule
  %       {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n)}
   %      {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0
%\end{align*}

@@

%\TODO{Je ne peux pas refaire tourner le code, il faut que je modifie le pNet Editor pour qu'ils n'utilise plus les variables d'etat... Donc les 3 prochaines pages sont obsoletes...}
%% \TODO{keep ?}
%% \paragraph{Variable management.}
%% The variables in each synchronisation vector are considered local:
%% for a given pNet expression, we must have fresh local variables for
%% each occurrence of a vector (i.e. each time we instantiate rule
%% \TrDeux). Similarly the state variables of each copy of a
%% given pLTS in the system, must be distinct, and those created for each
%% application of \TrDeux\ have to be fresh and all distinct. 
%% This is implemented within the open-automaton generation algorithm,
%% using name generation using a global counter as a suffix.

@@

pLTS M1
  initial a0
  vars ?msg:Data ?c:Int
vars m_msg:Data m_ec:Int

@@

pLTS Sender
  initial s0
  vars ?msg:Data
vars  s_msg:Data s_ec:Int

@@

pLTS Receiver
  initial r0
  vars ?msg:Data ?c:Int
vars r_msg:Data r_ec:Int

@@

@@

It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviours.
More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
In this configuration we can guarantee that they are Weak bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this 
equivalence class of states as $\{000,202\}$.

% \TODO{May be express this property more formerly, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}

Full details of the weak transitions is listed here:

@@

All the following transitions are parametrized by an integer $n\in \mathcal{N}$, meaning they stand for the (infinite) set of weak OTs. 
In some cases, this set is further restricted (see e.g. $WI_{7b}(n)$), in which case we have added an explicit quantifier.
\smallskip

@@

$ WI_5(n) = \openrule
         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {210 \OTWeakarrow {\tau} 220}
         $

$ WI_{5a}(n) = \openrule
         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
         {210 \OTWeakarrow {\tau} 100}
         $

@@

\medskip
$ WI_7(n) = \openrule
         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
         {210 \OTWeakarrow {\tau} 201}
         $

$ WI_{7a}(n) = \openrule
         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{m\_ec}+n)}
         {220 \OTWeakarrow {\tau} 201}
         $

$ \forall n\ge 1. WI_{7b}(n) = \openrule
         {\{\}, True, (\texttt{r\_msg}\gets \texttt{m\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\tau} 201}
         $

$ WI_8 = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec)}\}, True, ()}
         {201 \OTWeakarrow {\nounderline{\texttt{out(r1-msg,r1-ec)}}} \{202, 000\}}
         $

$ \forall n\ge 1. WI_{8a}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(m\_msg,m\_ec}+n)\}, True, ()}
         {210 \OTWeakarrow {\nounderline{\texttt{out(m\_msg,m\_ec}+n)}} \{202, 000\}}
         $

 $ \forall n\ge 1.  WI_{8b}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s\_ec}+n)\}, True, ()}
         {220 \OTWeakarrow {\nounderline{\texttt{out(??\_msg,m\_ec}+n)}} \{202, 000\}}
         $

 $ \forall n\ge 1.  WI_{8c}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, ()}
         {100 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} \{202, 000\}}
         $

@@

\bigskip
Considering the first triple <b0, 000, True>, we have to prove the following properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense of definition \ref{def-Weak-bisim}, by the weak transition $WOT$ (it could be a set, but this will not be used here):

@@
